\section{Current System}

The current system is an Excel based application which facilitates searches on an academic topic. The system does not contain articles directly but holds data regarding the content of the article. 
The system supports multiple users to contribute data and makes it possible to identify if another user is contributing data on the same article. The contributed data is mostly keywords which makes it easier to search and compare articles. To search for articles, a user must submit keywords, which the articles will be ranked after. Articles are also ranked after the amount of keywords they have in common with other articles. The current system can work, but becomes increasingly hard to manage. Thus, a new system which solves the negatives while keeping all of the functionality that the system already supports is recommended. This can be done with a separation of the data and the user interface, by creating a dedicated database and a dedicated user interface. This will ensure that new functionality will not be limited by the database structure. The negatives and pros of the current system are described below:


\subsection{Pros of current system}
The systems pros are as following:

\begin{enumerate}
	\item Excel licenses are cheap and are widely used by customer base
	\item Simple and easy to augment and implement changes.
	\item Data is safe from hostile users if excel files are read only. 
	\item It's easy to implement version control on .csv files. 
\end{enumerate}

\subsection{Negatives of current system} 
And the systems Negatives are as following: 

\begin{enumerate}
	\item The data structures can be hard to manage, especially as the system grows in scope and content.
	\item The system does not support multiple users editing the same files at the same time.
	\item The system interface leaves a lot to be desired.
	\item New features becomes hard to implement as the system grows.
\end{enumerate}
