\section{\logtitle 12/01-2015} % Remember to set
\duration{9:00}{16:00}
\attend{\at}{\at}{\at}{\at}


\begin{itemize}
	\item [\textbf{Meeting pins:}]
	\item Testing strategy
	\item Shared data model required for use in repositories, stored model entities and testing 
	\item Agreed on test syntax methodToTest\_condition\_expectedbehavior
     \item AutoMapper framework used to translate objects from application logic to DTO objects and Stored model entities
     \item Can now connect to a local database created from code first (AutoSysDbModel). Requires installation of SQL Server 2014 and login with (localdb)/myssql 
     \item Agreed to prepare questions and think about potential conflicts involving work of others when implementing things. We now put more focus on preparations before group work. Members are expected to prepare questions and identify potential challenges involving the work of others. 
     \item Reimplemented ids for entities in application logic where needed. 
\end{itemize}

\begin{itemize}
	\item [\textbf{Sprint Planning:}]
	\item Sections from Testing Strategy document has been assigned to individual group members. Expected template delivery on Thursday the 3rd of December. 
     \item Documentation boards on Trello are to be complete in order to clean up Trello for new tasks. 
\end{itemize}

\begin{itemize}
	\item [\textbf{Current work:}]
	\item Thor is currently working on implementing the Storage repositories containing CRUD operations for all model entities. He will first implement the tests for each repository. This is now possible due to the agreed data model (had conflict with Paper and Criteria entity). 
	\item Jacob is currently writing blackbox tests for the CriteriaHandler, working on a simple sorting operations which let a user sort Articles based on criterias and is working on Phase
\item William is curently working on Papermanagement and exploring the nUnit framework (Which help reducing redundant test cases).
\item Dennis working on black box testing and Fasades
\end{itemize}