\section{\logtitle 12/14-2015} % Remember to set
\duration{9:00}{16:00}
\attend{\at}{\at}{\at}{\at}


\begin{itemize}
	\item [\textbf{Meeting pins:}]
	\item UI should be done.
	\item Integration test of backend (database, mapping, web api and UI backend).
	\item ODD design patterns and class descriptions. 
	\item RAD and SDD cleanup. 
\end{itemize}

\begin{itemize}
	\item [\textbf{Sprint Planning:}]
	\item Jacob is working on Web API and communication to Application Logic layer.
	\item Dennis is almost done with UI front end and will start on UI backend. 
	\item Thor is finishing Adapters and fixing dependency injection of repositories in adapters. He will optionally make AutoMapper profiles convert entities from logic to storage. 
	\item William is working on BibTex parser and tests. 
\end{itemize}

\begin{itemize}
	\item [\textbf{Tomorrow plan :}]
	\item Thor is making integration test of database with EF and repositories (either a separate local test database with new connection string or in-memory using Effort framework. 
	\item Dennis is reworking UI and implementing backend. 
	\item Jacob is still finishing Web Api. 
	\item William is working on Study Configuration logic (upload and parsing bibtex, criteria, datafields and phases for creating studies). 
\end{itemize}

\begin{itemize}
	\item[\textbf{Goal : }]
	\item UI is required to create a study and backend needs serious work from Dennis.
	\item Application logic to be implemented by William and Thor. 
	\item Jacob has to finish Web Api. 
\end{itemize}